---
title: "TSST LMM"
author: "AGC"
date: "15 4 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(haven)
library(tidyverse)
library(data.table)
library(lme4)
library(kableExtra)
library(caret)
library(ggplot2)
library(compareGroups)

home = "S:/KJP_Biolabor/Projekte/FemNAT-CD/TSST_Analysis"

```

# Prepare

## read and check data 

```{r preprocess}
df = as.data.frame(read_sav(paste0(home,"/data/13.04.2021_290_170_CORTAUCsplit.sav")))

df$group = drop(factor(df$group, levels = c(1,2), labels=c("CD", "CTRL"))) %>% relevel(., ref="CTRL")
df$centre = drop(factor(df$centre, levels = c(1,2,3,4,5), labels=c("FFM", "AAC", "BLB", "BCN", "SZG")))
df$any_med_ccept = drop(factor(df$any_med_ccept, levels = c(0,1), 
                               labels=c("no_med", "med")))%>% relevel(., ref="no_med")
df$smoking_yes_no = drop(factor(df$smoking_yes_no, levels = c(0,1), 
                                labels=c("no_smk", "smk")))%>% relevel(., ref="no_smk")
df$gender = drop(factor(df$gender, levels = c(1,2), 
                        labels=c("male", "female")))%>% relevel(., ref="male")

table(df$group, useNA = "always")
table(df$centre, useNA = "always")
table(df$any_med_ccept, useNA = "always")
table(df$smoking_yes_no, useNA = "always")
table(df$gender, useNA = "always")

UV = c("centre","age_meancentered", "explstart_meancentered_min", 
  "BMI_imp_meancentered", "any_med_ccept", "smoking_yes_no", "gender", "group")


AV = list(
AV_stressed = c(stressed_1=1, stressed_2=2,
                stressed_3=3, stressed_4=4,
                stressed_5=5, stressed_6=6, 
                stressed_7=7, stressed_8=8), 
AV_CORT = c(CORT_BL_log=0, CORT_10_log=10, CORT_25_log=25, CORT_40_log=40, CORT_55_log=55) ,
AV_TEST = c(TEST_BL_log=0, TEST_10_log=10, TEST_55_log=55),
AV_OXT =  c(OXT_BL_log=0, OXT_1_log=1, OXT_10_log=10) )



model = "DV~1+centre+age_meancentered+explstart_meancentered_min+BMI_imp_meancentered+any_med_ccept+smoking_yes_no+gender+group+Time+gender*group+Time*group+gender*Time*group+(1|twuid)"

# do not include site in correlation plot 

tmpframe = df[,UV[!UV%in% c("centre")]] %>% mutate_if(is.factor, function(x) as.numeric(x)-1)

corrplot::corrplot(cor(tmpframe, use = "pairwise"))
```

## complete cohort descriptives

```{r preprocess_allstat}
res = compareGroups(group~., data = df[,UV])
#summary(res)
export_table <- createTable(res)
export_table
```

## male only cohort descriptives
```{r preprocess_malestat}
res = compareGroups(group~., data = df[,UV], subset = gender=="male")
export_table <- createTable(res)
export_table
```

## female only cohort descriptives
```{r preprocess_femalestat}
res = compareGroups(group~., data = df[,UV], subset = gender=="female")
export_table <- createTable(res)
export_table

```


## Definitions

**IV of interest :**

* Gruppe ("group") 
* sex ("gender")
* Zeitpunkt ("Time")
* Gruppe x Zeitpunkt
* Gruppe x sex

**IV of no interest :** 

* Site ("centre")
* Age scaled ("age_meancentered")
* "explstart_meancentered_min" 
* "BMI_imp_meancentered"
* "any_med_ccept"
* "smoking_yes_no"

**DV:**

* psychologischer Stress („stressed“)
* Cortisol („CORT“)
* Testosteron („TEST”) 
* Oxytocin (OXT”)


## linear model with mixed effects 

We adapted a boxed design by individual over Time

full model: `r model`


```{r mml, warning=FALSE}
resall = list()

for (depvar in names(AV)){
  cols = names(AV[[depvar]])
  long = df[,c("twuid",cols, UV)] %>% 
    gather(key = "value", value = "DV", all_of(cols))
  long$Time = AV[[depvar]][long$value]
  long$twuid = as.factor(long$twuid)
  model.lme = lme4::lmer(model, data=long)
  model.lme0 = lme4::lmer(DV~1+(1|twuid), data=long)
  anovah0 = anova(model.lme0, model.lme)
  model_p_val = anovah0$`Pr(>Chisq)`[2]
  Res = summary(model.lme)
  resall[[depvar]] = model.lme
  resall[[paste0(depvar,"_longdat")]] = long
  res.coeff = as.data.frame(Res$coefficients)
  res.coeff$pvalue = pt(abs(res.coeff$"t value"), 1000000, lower.tail = F) * 2
  resall[[paste0(depvar,"_coeff")]]=res.coeff
  resall[[paste0(depvar,"_modsig")]]=model_p_val
}

```

# Results 

## stressed

overall model p-value (h0 model: stressed~1+(1|twuid)):
`r as.character(signif(resall[["AV_stressed_modsig"]],3))`

```{r, war}
tableplot = function (x){
  x %>% dplyr::mutate_if(is.numeric, function(x){as.character(signif(x, 3))}) %>% kbl() %>% kable_classic()
  }


depvar = "AV_stressed"

resall[[paste0(depvar, "_coeff")]] %>% tableplot()

ggplot(data = resall[[paste0(depvar, "_longdat")]], 
       aes(DV, group=Time, col=Time)) + 
  ylab("density") + xlab(depvar)+
  geom_density()

ggplot(data = resall[[paste0(depvar, "_longdat")]], 
       aes(Time,DV, col=group)) + 
  ylab(depvar) + xlab("Time")+
  geom_smooth(method = 'loess') + geom_point() +   facet_wrap(~gender)




```

## CORT

overall model p-value (h0 model: CORT~1+(1|twuid)):
`r as.character(signif(resall[["AV_CORT_modsig"]], 3))`

```{r}
depvar = "AV_CORT"

resall[[paste0(depvar, "_coeff")]] %>% tableplot()

ggplot(data = resall[[paste0(depvar, "_longdat")]], 
       aes(DV, group=Time, col=Time)) + 
  ylab("density") + xlab(depvar)+
  geom_density()

ggplot(data = resall[[paste0(depvar, "_longdat")]], 
       aes(Time,DV, col=group)) + 
  ylab(depvar) + xlab("Time")+
  geom_smooth(method = 'loess') + geom_point()+   facet_wrap(~gender)

  

```

## TEST

overall model p-value (h0 model: TEST~1+(1|twuid)):
`r as.character(signif(resall[["AV_TEST_modsig"]], 3))`


```{r}
depvar = "AV_TEST"

resall[[paste0(depvar, "_coeff")]] %>% tableplot()

ggplot(data = resall[[paste0(depvar, "_longdat")]], 
       aes(DV, group=Time, col=Time)) + 
  ylab("density") + xlab(depvar)+
  geom_density()

ggplot(data = resall[[paste0(depvar, "_longdat")]], 
       aes(Time,DV, col=group)) + 
  ylab(depvar) + xlab("Time")+
  geom_smooth(method = 'loess') + geom_point()+   facet_wrap(~gender)


```

## OXT

overall model p-value (h0 model: OXT~1+(1|twuid)):
`r as.character(signif(resall[["AV_OXT_modsig"]], 3))`

```{r}

depvar = "AV_OXT"

resall[[paste0(depvar, "_coeff")]] %>% tableplot()

ggplot(data = resall[[paste0(depvar, "_longdat")]], 
       aes(DV, group=Time, col=Time)) + 
  ylab("density") + xlab(depvar)+
  geom_density()

ggplot(data = resall[[paste0(depvar, "_longdat")]], 
       aes(Time,DV, col=group)) + 
  ylab(depvar) + xlab("Time")+
  geom_smooth(method = 'loess') + geom_point()+   facet_wrap(~gender)
  

```

